Towards open collaboration in biomedical and health research: An open collaborative scoping review

### 2023-10-06 doc/paper.qmd
rename title of paper

---
title: "Towards open collaboration in biomedical and health research: A scoping review"
date: last-modified
author: 
  - name: Hannah Chatwin
    affiliations: 
      - ref: au
  - name: Mario Garcia
    affiliations: 
      - ref: ku
  - name: Daniel B. Ibsen
    affiliations: 
      - ref: sdca
      - ref: au
  - name: Luke W. Johnston
    affiliations: 
      - ref: sdca
      - ref: au
affiliations:
  - id: sdca
    name: Steno Diabetes Center Aarhus
    country: Denmark
  - id: au
    name: Aarhus University
    country: Denmark
  - id: ku
    name: Copenhagen University
    country: Denmark
format: html
---

>>>>

---
title: "Towards open collaboration in biomedical and health research: An open collaborative scoping review"
date: last-modified
author: 
  - name: Hannah Chatwin
    affiliations: 
      - ref: au
  - name: Mario Garcia
    affiliations: 
      - ref: ku
  - name: Daniel B. Ibsen
    affiliations: 
      - ref: sdca
      - ref: au
  - name: Luke W. Johnston
    affiliations: 
      - ref: sdca
      - ref: au
affiliations:
  - id: sdca
    name: Steno Diabetes Center Aarhus
    country: Denmark
  - id: au
    name: Aarhus University
    country: Denmark
  - id: ku
    name: Copenhagen University
    country: Denmark
format: html
---
